Research paper

### 2013-01-02 Research paper.tex
Final things for first draft.

I should add that translation system focussing on one such approach are rare. As \citet{jm09} put it: 'Real systems tend to involve combinations of elements from these three architectures; thus, each is best thought of as a point in an algorithmic design space rather than as an actual algorithm.' The Systran system (\citealp{hs92,senellartea01}) is an example of this.\\\indent %TODO example of what
An advantage of the rule-based approach is that one has a lot of control over the output. In theory, if something has gone wrong, all one has to do is find out which rule or dictionary item caused the problem and improve it. In practice, however, it is almost impossible to have a dictionary and rule system good enough for more complicated sentences, and things like rule interactions and ambiguity make everything even more complicated. The next two approaches therefore replace hand-crafted rules with automatically generated ones.

@@

\bibitem[Hutchins \& Somers, 1992]{hs92}
Hutchins \& Somers, 1992.

@@

\bibitem[Senellart et al., 2001]{senellartea01}
Senellart et al., 2001

@@

\end{thebibliography}
% Documentatie Colibri

>>>>

I should add that translation system focussing on one such approach are rare. As \citet{jm09} put it: 'Real systems tend to involve combinations of elements from these three architectures; thus, each is best thought of as a point in an algorithmic design space rather than as an actual algorithm.' The Systran system \citep{hs92,senellartea01}, for example combines the first three approaches.\\\indent
An advantage of the rule-based approach is that one has a lot of control over the output. In theory, if something has gone wrong, all one has to do is find out which rule or dictionary item caused the problem and improve it. In practice, however, it is almost impossible to have a dictionary and rule system good enough for more complicated sentences, and things like rule interactions and ambiguity make everything even more complicated. The next two approaches therefore replace hand-crafted rules with automatically generated ones.

@@

\bibitem[Van Gompel, 2012]{vangompel12}
Van Gompel, M. (2012). \emph{Colibri documentation}. Available online at http://proycon.github.com/colibri/doc/.

\bibitem[Hutchins \& Somers, 1992]{hs92}
Hutchins, W. J. \& H. L. Somers (1992). \emph{An introduction to Machine Translation.} Academic Press.

@@

\bibitem[Senellart et al., 2001]{senellartea01}
Senellart, J., P. Dienes \& T. Varadi (2001). New generation SYSTRAN translation system. In emph{MT Summit 8}.

@@

\end{thebibliography}
